---
title: "Turbine Information Report: `r params$n`"
author: "https://mikeyharper.shinyapps.io/windturbinemap/"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    fig_caption: true
classoption: a4paper
fontsize: 11pt
geometry: margin=1in
params:
  n: NA
---

```{r LoadData, include=FALSE}

# Dont display code
knitr::opts_chunk$set(echo = FALSE, tidy = TRUE, tidy.opts=list(width.cutoff=60), comment = ">")

# Filter the data for the turbine of interest
REPD <- read.csv("https://raw.githubusercontent.com/mikey-harper/ShinyApps/master/WindTurbineMapUK/TurbineAllData.csv", stringsAsFactors = FALSE)

TurbineData <- REPD[REPD$Ref.ID == params$n,]
```

This report provides a detailed breakdown of Wind Turbine planning application number **`r TurbineData$Planning.Application.Reference`**. The site location is:

- **Address**:   `r TurbineData$Address`
- **County**:    `r TurbineData$County`
- **Post Code**: `r TurbineData$Post.Code`
- **Region**:    `r TurbineData$Region`
- **Country**    `r TurbineData$Country`

# Planning Information

```{r}

TurbineFiltered <- as.data.frame(t(TurbineData))
names(TurbineFiltered) <- c("Value")

# Only put variables with values into table
knitr::kable(na.omit(TurbineFiltered), caption = "Full Site Information")
```

**Values with data missing**:

`r names(TurbineData[,is.na(TurbineData)])`

# Site Location

The maps show the location of the wind turbine site:

```{r, fig.cap="Regional Maps", message=FALSE, warning=FALSE, out.width="100%", fig.pos='!h'}
library(ggmap)
library(gridExtra) # For arraning results side by side
# devtools::install_github('oswaldosantos/ggsn')
# library(ggsn)

# National Zoom Map
maptile1 <- get_map(location = "Great Britain", zoom=5)

map1 <- ggmap(maptile1) +
  geom_point(aes(x = lon, y = lat), data = TurbineData, alpha = .5) +
  theme_nothing() +
  ggtitle("National")

# Regional Zoom Map
maptile2 <- get_map(location = c(TurbineData$lon, TurbineData$lat), zoom = 10)

map2 <- ggmap(maptile2) +
  geom_point(aes(x = lon, y = lat), data = TurbineData, alpha = .5) +
  theme_nothing()

# Local Map
maptile3 <- get_map(location = c(TurbineData$lon, TurbineData$lat), zoom = 12)

map3 <- ggmap(maptile3) +
  geom_point(aes(x = lon, y = lat), data = TurbineData, alpha = .5) +
  theme_nothing()

# Local Satellite

maptile4 <- get_map(location = c(TurbineData$lon, TurbineData$lat), zoom = 12, maptype = "satellite", source = "google")

map4 <- ggmap(maptile4) +
  geom_point(aes(x = lon, y = lat), data = TurbineData, alpha = .5) +
  theme_nothing()

grid.arrange(map1, map2, nrow = 1)
```

```{r fig.cap="Local Maps", message=FALSE, warning=FALSE, out.width="100%", fig.pos='!h'}

grid.arrange(map3, map4, nrow = 1)

```

The following link can be clicked to load the site location within google maps: 

**Link to be added**

## Site Statistics

The following statistics are based on the statistical analysis completed by (Michael Harper)[https://eprints.soton.ac.uk/408181/]: 

## Predicted Success Rates

```{r}
library(ggplot2)

ggplot(data = TurbineData) + geom_col(aes("Success Chance", Site.Score*100)) +
  coord_flip() +
  scale_y_continuous(limits = c(-0, 100))

```


## Site Comparison##

**To be added: a comparison of how the compares against the national average**

