---
title: "Turbine Information Report: `r params$n`"
author: "https://mikeyharper.shinyapps.io/windturbinemap/"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    fig_caption: true
classoption: a4paper
fontsize: 11pt
geometry: margin=1in
params:
  n: NA
---

This report provides the full data output for a wind turbine planning application within the UK. The location data was used within the analysis *"Identifying key influences for planning acceptance of onshore wind turbines"* and is available to read here: [https://eprints.soton.ac.uk/408181/](https://eprints.soton.ac.uk/408181/)

```{r LoadData, include=FALSE}
# Dont display code
knitr::opts_chunk$set(echo = FALSE, tidy = TRUE, tidy.opts=list(width.cutoff=60), comment = ">")


REPD <- read.csv("https://raw.githubusercontent.com/mikey-harper/ShinyApps/master/WindTurbineMapUK/data/TurbineAllData.csv", stringsAsFactors = FALSE)


knitr::opts_chunk$set(echo = FALSE, tidy = TRUE, tidy.opts=list(width.cutoff=60), comment = ">")

# --- Packages

library(tidyverse)
library(ggplot2)
library(reshape2)
library(knitr)

VariableDisplay <- read.csv("https://raw.githubusercontent.com/mikey-harper/ShinyApps/master/WindTurbineMapUK/data/VariableDisplayNames.csv")


# --- Functions
matchNames <- function(inputNames){
    # Matches variable names with their full descriptive name. Used when plotting or showing
    # results in a table
    #
    names <- VariableDisplay
    return(names[match(x = inputNames, table = names$Label, nomatch = ""), 2])
  }

RenamesColumns <- function(dataframe, dropNA = FALSE){
  # Checks the row names against the variable full names
  #
  ReplacementNames <- matchNames(names(dataframe))
  names(dataframe) <- ReplacementNames
  if(dropNA){dataframe <- dataframe[,-c(which(ReplacementNames == ""))]}
  return(dataframe)
}
```

```{r FilterDataset, message=FALSE, warning=FALSE}
TurbineData <- REPD[REPD$Ref.ID == params$n,]
Turbines_Proximity <- TurbineData[, 46:64] %>% RenamesColumns() %>% melt()
Turbines_Political <- TurbineData[, 79:82] %>% RenamesColumns() %>% melt()



```

This report provides a detailed breakdown of Wind Turbine planning application number **`r TurbineData$Planning.Application.Reference`**. 

# Basic Details of Site

- **Address**:   `r TurbineData$Address`
- **County**:    `r TurbineData$County`
- **Post Code**: `r TurbineData$Post.Code`
- **Region**:    `r TurbineData$Region`
- **Country**    `r TurbineData$Country`

**Planning Status**:  `r TurbineData$Development.Status`

# Project Size

The planning permission was for **`r TurbineData$Capacity`MW** with a total of **`r TurbineData$No..of.Turbines`** wind turbines. The last time the record was updated was on **`r TurbineData$Record.Last.Updated..dd.mm.yyyy.`**.
 
# Site Proximity

Figure 1 highlights the proximity of the site to the nearest faeatures which have beeen indicated as potentially influential within the acceptance rates of wind turbines.

```{r ProximityPlot, fig.cap="Proximity of site to features", fig.asp=0.4}
Turbines_Proximity <- Turbines_Proximity[order(Turbines_Proximity$value), ]

ggplot(data = Turbines_Proximity, aes(reorder(variable, value, FUN = median) , value)) +
  geom_bar(stat="identity", 
           aes(fill = reorder(variable, value, FUN = median)),
           col = "black", size = 0.2) +
  scale_fill_discrete(grDevices::cm.colors(n = 20)) +
  theme(legend.position = "none") +
  labs(x="", y = "Distance (km)") +
  coord_flip()
```

# Site Location

Figure 2 maps show the location of the wind turbine site.

```{r SiteLocations, fig.cap="Regional Maps", message=FALSE, warning=FALSE, out.width="100%", fig.pos='!h'}

library(ggmap)
library(gridExtra) # For arranging results side by side
# devtools::install_github('oswaldosantos/ggsn')
# library(ggsn)

margin <- theme(plot.margin = unit(c(0.2,0.2,0.2,0.2), "cm"))

# National Zoom Map
maptile1 <- get_map(location = "Great Britain", zoom=5)

map1 <- ggmap(maptile1) +
  geom_point(aes(x = lon, y = lat), data = TurbineData, alpha = .5) +
  theme_nothing() +
  ggtitle("National") +
  margin

# Local Map
maptile3 <- get_map(location = c(TurbineData$lon, TurbineData$lat), zoom = 12)

map3 <- ggmap(maptile3) +
  geom_point(aes(x = lon, y = lat), data = TurbineData, alpha = .5) +
  theme_nothing() +
  margin

grid.arrange(map1, map3, nrow = 1)

```


# Features to add

- How does the site compare to other projects?
- Build a graph of the planning status dates within GraphViz
- Add a breakdown of the political and demographic data
- More graphs to represent trends